Multidimensional analysis and detection of informative features in human brain white matter

### 2021-02-06 reports/manuscript/paper.tex
Remove subsection numbering for Software implementation
Proposed changes to the author summary.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
\todo[inline]{Write author summary}

\linenumbers

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.
\section*{Author summary}
The connections between different parts of the brain form networks that are
important for information transmission and for brain health. These connections
are composed of nerve fibers that travel through the white matter portion of the
brain. Thus, mapping tissue properties in white matter pathways can help us
understand which connections and what tissue properties are relevant to brain
diseases, or explain differences in behavior and cognition between different
individuals. We developed a new statistical method that helps map the white
matter by automatically identifying the features of the white matter that
correspond to individual differences. Our approach relies on incorporating our
knowledge of the anatomical sub-divisions of the white matter into the
statistical model itself. We demonstrate that the model accurately captures
differences between individual's with amyotrophic lateral sclerosis (ALS) and
healthy controls. It also accurately captures brain changes that correspond with
the ages of different individuals. We tested our method on four different
datasets and found that it is more accurate than previous methods used with
these datasets, while also allowing us to highlight which white matter tissue
properties and which connections account for individual differences, thus
providing interpretable results.
\linenumbers
